### 2011-04-07 standing-patches-paper.tex
added convergence notes

Suppose we fix our attention on a particular new mutation that happens to be the first to occur in some region.
As it spreads, it will cover a distance $L$ in time $L/v$, where $v = \sigma \sqrt{2s}$ is the speed of the wave of advance.
The number of other mutations appearing in the circle it has covered up until this time is Poisson with mean
$\lambda_0 \pi L^2 + \lambda \pi L^3 /v$ in two dimensions
(and $\lambda_0 2 L + \lambda \pi L^2 /v$ in one dimension).
% $\lambda_0 \omega_d L^d + \lambda \omega_d L^{d+1} /v$ in $d$ dimensions
Therefore, if we define $\chi$ to be the unique positive solution to
$\lambda_0 \pi \chi^2 + \lambda \pi \chi^3 /v = 1$,
then $\chi$ gives the distance spread unobstructed by the descendants of a new mutant
before it is expected that one other successful mutation would have arisen in the area covered so far.
If we define $u = 2 \pi^3 \lambda_0^3 - 27 \pi^2 v^2 \lambda^2$,
The solution to this is {\color{red} XXX what?}
(In one dimension the characteristic length is $\chi = \frac{ \sqrt{ 4 \lambda_0^2 + 2\lambda v } - 2 \lambda_0 }{ 4 \lambda v }$.)

@@

The quantity that is perhaps easiest to compute is the mean time until adaptation.
Fix some geographic location, and let $\tau\ge0$ be the time at which the point is reached by the advantageous mutations.
Then, as shown in Figure XX,
$\tau > t$ if and only if the cone with point at $(x,t)$ and slope $v$ extending back to $t=0$ is empty of successful mutations.
Since we assume these are a Poisson process, 
\[
    \P\{ \tau > t \} = \exp\left( - \lambda_0 \pi v^2 t^2 - \lambda \pi v^2 t^3 ) ,
\]
and so we have
\begin{align}
    \E[\tau] % &= \int_0^\infty \P\{ \tau > t \} dt \\
        &= \int_0^\infty \exp\left( - \lambda_0 \pi v^2 t^2 - \lambda \pi v^2 t^3 ) dt .
\end{align}

>>>>

Suppose we fix our attention on a particular new mutation that happens to be the first to occur in some region.
As it spreads, it will cover a distance $L$ in time $L/v$, where $v = \sigma \sqrt{2s}$ is the speed of the wave of advance.
The number of other mutations appearing in the circle it has covered up until this time is Poisson with mean
$\lambda_0 \pi L^2 + \lambda \pi L^3 /v$ in two dimensions
(and $\lambda_0 2 L + \lambda \pi L^2 /v$ in one dimension).
% $\lambda_0 \omega_d L^d + \lambda \omega_d L^{d+1} /v$ in $d$ dimensions
Therefore, if we define $\chi$ to be the unique positive solution to
$\lambda_0 \pi \chi^2 + \lambda \pi \chi^3 /v = 1$,
then $\chi$ gives the distance spread unobstructed by the descendants of a new mutant
before it is expected that one other successful mutation would have arisen in the area covered so far.
If we define $u = 2 \pi^3 \lambda_0^3 - 27 \pi^2 v^2 \lambda^2$,
The solution to this is {\bf XXX what?}
(In one dimension the characteristic length is $\chi = \frac{ \sqrt{ 4 \lambda_0^2 + 2\lambda v } - 2 \lambda_0 }{ 4 \lambda v }$.)

@@

The quantity that is perhaps easiest to compute is the mean time until adaptation.
Fix some geographic location, and let $\tau\ge0$ be the time at which the point is reached by the advantageous mutations.
Then, as shown in Figure XX,
$\tau > t$ if and only if the cone with point at $(x,t)$ and slope $v$ extending back to $t=0$ is empty of successful mutations.
Since we assume these are a Poisson process, 
\[
    \P\{ \tau > t \} = \exp\left( - \lambda_0 \pi v^2 t^2 - \lambda \pi v^2 t^3 \right) ,
\]
and so we have
\begin{align}
    \E[\tau] % &= \int_0^\infty \P\{ \tau > t \} dt \\
        &= \int_0^\infty \exp\left( - \lambda_0 \pi v^2 t^2 - \lambda \pi v^2 t^3 \right) dt .
\end{align}
